---
title       : Estimating Automobile Mileage
subtitle    : Exploring model fit
author      : anielsen108
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Estimating Automobile Mileage: Exploring model fit using a Shiny App

* The Shiny app allows you to explore the effect of including/excluding various variables from a linear model (without interaction) to see how this effects model fit. 

* Automobile mileage can be estimated as a linear effect of weight, 1/4 mile time, and Horsepower.

* App URL: https://anielsen108.shinyapps.io/ddp_app/

---

## Design of the Shiny App

````{r ShinyExcerpts, eval=FALSE}
# ui.R includes Checkbox Group Input to allow the user to select variables
checkboxGroupInput("variables", "Variables to Include",
                          c("Weight" = "wt",
                            "1/4 mile time" = "qsec",
                            "Horsepower" = "hp")),

# server.R stores these in array
variables <- eventReactive(input$fitButton, {input$variables})

# A formula for a linear model is built based on the variables checked.
formulaString <- "mpg ~"
if ("wt" %in% variables()) formulaString <- paste(formulaString, " wt +")
if ("qsec" %in% variables()) formulaString <- paste(formulaString, " qsec +")
if ("hp" %in% variables()) formulaString <- paste(formulaString, " hp +")
formulaString <- paste(formulaString, " 1 ")
           
fit <- lm(as.formula(formulaString), mtcars)
        
```

---

## Example 1: mpg predicted by weight

```{r Example1, echo=FALSE, fig.width = 6, fig.height=6}
        data(mtcars)
        fit <- lm(mpg ~ wt, mtcars)
        plot(mtcars$mpg,
                predict(fit, mtcars),
                main = paste("Linear Model: ", "mpg ~ wt"),
                xlab = "Actual MPG",
                ylab = "Predicted MPG")
         
                abline(0, 1, col="red")
         
   
```

---

## Example 2: mpg predicted by quarter mile time and horsepower
```{r Example2, echo=FALSE, fig.width = 6, fig.height=6}
        data(mtcars)
        fit <- lm(mpg ~ qsec + hp, mtcars)
        plot(mtcars$mpg,
                predict(fit, mtcars),
                main = paste("Linear Model: ", "mpg ~ gsec + hp"),
                xlab = "Actual MPG",
                ylab = "Predicted MPG")
         
                abline(0, 1, col="red")
   
```

---

## Conclusions: inclusion/exclusion matters

* As can be seen from these examples, the app allows the user to visually explore model fit for mileage estimation when including/excluding variables.

* Visually inspecting the fit is a good method to quickly see if there are any gross modelling errors.

* Check it out now! App URL: https://anielsen108.shinyapps.io/ddp_app/

